---
title: "Final Assignment"
author: "202338463"
date: "AT 2023"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # actually set the global chunk options.
```

```{r, include=FALSE}
library(spotifyr)
library(tidyr)
library(dplyr)
library(httr)
library(jsonlite)
library(plotly)
library(RSelenium)
library(rvest)
library(ggplot2)
library(stringr)
```

The Github repository of this report can be found
[here](https://github.com/busralb/MY472-Final.git). <br>

#### INTRODUCTION:

This study explores the current state of the musicians listed in Rolling
Stone Magazine's 100 greatest artists compilation. It investigates the
endurance of their engagement by analyzing metrics from Spotify. The
research quantifies listener engagement using follower counts and
popularity scores, hypothesizing that genre influences popularity.
Genres like rap and rock are expected to maintain high engagement, while
blues and soul, with smaller contemporary audiences, are anticipated to
be less popular. The study also examines decades and song features,
seeking correlations with ongoing popularity.

<br>

#### DATA:

The study utilizes data from four sources: 

Rolling Stone’s compilation was collected in segments due to the dynamic loading of the website.
After the top 50 were loaded, the top 50 were scraped by simulating
clicks on the 50-41 ranking range, and then these datasets were combined
in ‘greatest_100’.

While Spotifyr package provides convenient access to the Spotify API,
additional functions were created to manage the API rate limit
effectively. Specifically, the 'get_artist_info' is applied to the
'greatest_100' using for loop to extract genres, popularity and follower
counts. To address inconsistencies in names, an 'if' expression was
employed. Sub-genres were grouped under main headings, and artists with
multiple affiliations were categorized based on the most prominent. To
calculate average feature values for tracks, the
'get_artist_audio_features' function from Spotifyr package is utilized
in sequence to not exceed the rate.

As the API does not offer data regarding decades, the artists' active
years are scrapped from the All Media site. Then it was subsequently
processed using regular expressions, and was added to the
'greatest_100_info' as a column indicating the debut year of each
artist.

To evaluate the present popularity of artists featured in Rolling Stone
magazine, how many artists appeared on Billboard Artist chart throughout
2023 was tracked. It's worth noting that Billboard releases weekly
charts rather than monthly ones. Thus, data was specifically extracted
from the 3rd week of each month as representative. Also a helper
function and for loop were employed to compile the artists commonly
present in the Rolling Stone and Billboard rankings.

After data processing, three primary analysis datasets were generated:

‘greatest_100_info’: Contains artists’ names, genres, popularity scores,
followers, decades, and magazine rankings. ‘features_vs_popularity’:
Includes average values of artists’ music features. ‘billboard_artists’:
Subset of ‘greatest_100_info’ for artists in Billboard rankings.

<br> <br>

```{r, include=FALSE, cache = TRUE}
## Scrape the Rolling Stone's Compilation of the 100 greatest artists
# Start the Selenium server
rD <- rsDriver(browser = "firefox", verbose = FALSE, port = netstat::free_port(random = TRUE), chromever = NULL)
driver <- rD[["client"]]

# Specify the URL of the Rolling Stone page
rank_url <- "https://www.rollingstone.com/music/music-lists/100-greatest-artists-147446/"
driver$navigate(rank_url)

# Find the "Reject All" button and click it
reject_button <- driver$findElement(using = "css", value = "#onetrust-reject-all-handler")
reject_button$clickElement()

# Extract the HTML content of the entire page
page_source <- driver$getPageSource()

# Parse the HTML content with rvest
page <- read_html(page_source[[1]])

# Extract rank and name information
rank_elements <- page %>% html_nodes("span.c-gallery-vertical-album__number")
name_elements <- page %>% html_nodes("h2.c-gallery-vertical-album__title")

# Extract text from HTML nodes
ranks <- html_text(rank_elements)
names <- html_text(name_elements)

# Create a data frame with rank and name
artists_data <- data.frame(
  rank = as.integer(ranks),
  name = names,
  stringsAsFactors = FALSE
)

webElem <- driver$findElement("css", "body")
webElem$sendKeysToElement(list(key = "end"))

# Wait for some time to let the page load
Sys.sleep(5)

# Click on the "50 - 41" link to load the next set of artists
driver$findElement(using = "link text", value = "50 - 41")$clickElement()

# Wait for some time after clicking to allow content to load
Sys.sleep(5)

# Extract the HTML content of the page after clicking
page_source_next <- driver$getPageSource()

# Parse the HTML content with rvest for the next set of artists
page_next <- read_html(page_source_next[[1]])

# Extract rank and name information for the next set of artists
rank_elements_next <- page_next %>% html_nodes("span.c-gallery-vertical-album__number")
name_elements_next <- page_next %>% html_nodes("h2.c-gallery-vertical-album__title")

# Extract text from HTML nodes for the next set of artists
ranks_next <- html_text(rank_elements_next)
names_next <- html_text(name_elements_next)

# Create a data frame for the next set of artists
artists_data_next <- data.frame(
  rank = as.integer(ranks_next),
  name = names_next,
  stringsAsFactors = FALSE
)

# Close the RSelenium server
rD[["server"]]$stop()

# Merge the data frames using rbind
greatest_100 <- rbind(artists_data, artists_data_next)
```

```{r, include=FALSE, cache = TRUE}
## Define functions to use to access Spotify API and with spotifyr package
# Read the API KEY
readRenviron("~/Desktop/myenvs/spotify.env")

apikey <- Sys.getenv("SPOTIFY_CLIENT_SECRET")
access_token <- get_spotify_access_token()

# Function to get artist information by name
get_artist_info <- function(artist_name) {
  access_token <- get_spotify_access_token()
  
  # Spotify API endpoint for artists
  artist_endpoint <- paste0("https://api.spotify.com/v1/search?q=",
                            URLencode(artist_name), "&type=artist&limit=1")
  
  # Make GET request to the Spotify API
  response <- GET(
    url = artist_endpoint,
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  stop_for_status(response)
  
  # Parse JSON response
  artist_info <- content(response, "parsed")
  
  # Extract relevant information
  artist_data <- data.frame(
    name = artist_info$artists$items[[1]]$name,
    genres = toString(artist_info$artists$items[[1]]$genres),
    popularity = toString(artist_info$artists$items[[1]]$popularity),
    followers_total = artist_info$artists$items[[1]]$followers$total,
    stringsAsFactors = FALSE
  )
  
  return(artist_data)
}

# Function to get artist ID by name
get_artist_id <- function(artist_name) {
  access_token <- get_spotify_access_token()
  
  # Spotify API endpoint for artists
  artist_endpoint <- paste0("https://api.spotify.com/v1/search?q=",
                            URLencode(artist_name), "&type=artist&limit=1")
  
  # Make GET request to the Spotify API
  response <- GET(
    url = artist_endpoint,
    add_headers(Authorization = paste("Bearer", access_token))
  )
  stop_for_status(response)
  
  # Parse JSON response
  artist_info <- content(response, "parsed")
  
  # Extract relevant information
  artist_id <- artist_info$artists$items[[1]]$id
  
  return(artist_id)
}

function(artist_id, country_code = "US") {
  access_token <- get_spotify_access_token()
  endpoint <- paste0("https://api.spotify.com/v1/artists/", artist_id, "/top-tracks")
  
  response <- GET(
    endpoint,
    add_headers("Authorization" = paste("Bearer", access_token)),
    query = list(country = country_code, limit = 10),
    verbose()
  )
  
  stop_for_status(response)
  
  tracks_data <- content(response)$tracks
  
  tracks_df <- data.frame(
    name = sapply(tracks_data, function(track) track$name),
    popularity = sapply(tracks_data, function(track) track$popularity),
    id = sapply(tracks_data, function(track) track$id),

    stringsAsFactors = FALSE
  )
  
  return(tracks_df)
}
```

### ANALYSIS:

[**Fig.1:** *The graph depicts Spotify popularity scores of artists with
their corresponding ranks. Each bubble is color-coded based on genre,
and the size is determined by the follower count on
Spotify.*]{style="display: block; text-align: center; font-size: small;"}

```{r, out.width='100%', fig.align='center'}
# Create an empty list to store the results
artist_info_list <- list()

# Iterate over each row in greatest_100
for (i in 1:nrow(greatest_100)) {
  # Get the artist name and rank from the current row
  artist_name <- greatest_100$name[i]
  artist_rank <- greatest_100$rank[i]
  
  # Handle the special case for "Parliament and Funkadelic"
  if (artist_name == "Parliament and Funkadelic") {
    # Call get_artist_info("Parliament") and store the result
    artist_info <- get_artist_info("Parliament")
  } else {
    # Call get_artist_info() with the current artist name and store the result
    artist_info <- get_artist_info(artist_name)
  }
  
  # Add the rank to the artist_info data frame
  artist_info$rank <- artist_rank
  
  # Add the result to the list
  artist_info_list[[i]] <- artist_info
}

# Convert the list of data frames to a single data frame
greatest_100_info <- do.call(rbind, artist_info_list)

# Group genres under main headings 
greatest_100_info <- greatest_100_info %>%
  mutate(genres = case_when(
    grepl("hip-hop", tolower(genres)) | grepl("hip hop", tolower(genres)) | grepl("rap", tolower(genres)) ~ "rap",
    grepl("rock", tolower(genres)) | grepl("punk", tolower(genres)) ~ "rock",
    grepl("blues", tolower(genres)) ~ "blues",
    grepl("soul", tolower(genres)) | grepl("motown", tolower(genres)) ~ "soul",
    grepl("pop", tolower(genres)) | grepl("reggae", tolower(genres))  ~ "pop",
    grepl("country", tolower(genres)) ~ "country",
    grepl("reggae", tolower(genres)) ~ "reggae",
    TRUE ~ genres
  )) %>%  
  
mutate(genres = ifelse(name == "Muddy Waters", "blues", genres),
         genres = ifelse(name == "The Drifters", "blues", genres),
         genres = ifelse(name == "Fats Domino", "blues", genres),
         genres = ifelse(name == "The Shirelles", "soul", genres),
         genres = ifelse(name == "Jackie Wilson", "soul", genres),
         genres = ifelse(name == "Michael Jackson", "pop", genres))

greatest_100_info$popularity <- as.numeric(greatest_100_info$popularity)

# Create the bubble chart
popularity_vs_genre <- plot_ly(
  data = greatest_100_info,
  x = ~rank,
  y = ~popularity,
  type = "scatter",
  text = ~name,
  color = ~genres,
  mode = "markers",
  size = ~followers_total,
  fill = ~'',
  marker = list(sizemode = "diameter", opacity = 0.7),
  colors = viridis::viridis(20)
) %>%
  layout(
    title = "Artist Popularity and Follower Counts",
    xaxis = list(
      title = "Rolling Stone Ranking",
      range = c(-5, max(greatest_100_info$rank) + 5),
      zeroline = FALSE
    ),
    yaxis = list(
      title = "Popularity Score",
      range = c(0, max(greatest_100_info$popularity) + 15),tickmode = "linear", 
      dtick = 10 
    ),
    showlegend = TRUE
  )

# Show the bubble chart
popularity_vs_genre
```

Spotify provides popularity score for artists, based on the average of
plays and how recent those plays are. This combined with follower
counts, offer insights into listener engagement. The clustering of
artists in the 50-85 popularity range suggests sustained interest in
their music. Notably, artists with rap songs, positioned towards the end
of the list, have higher average popularity scores, with Eminem leading.
Rock artists have an average popularity score of approximately 68.38,
while soul, blues, and country artists are among the least popular by
the end of 2023.

```{r}
# Function to navigate to the URL and accept cookies
#navigate_and_accept_cookies <- function() {
#  # Initialize the RSelenium driver
#  rD <- rsDriver(browser = "firefox", verbose = FALSE, port = netstat::free_port(random = TRUE), chromever = NULL)
#  driver <- rD[["client"]]
#  # Navigate to the AllMusic search page
#  driver$navigate("https://www.allmusic.com/search/all/")
  
#  # Wait for 1 second before clicking the "AGREE" button
#  Sys.sleep(1)
  
#  agree_button <- driver$findElement(using = "css selector", value = ".fc-cta-consent")
  
#  # Click the "AGREE" button
#  agree_button$clickElement()
#  return(driver)
#}

# Function to scrape artist decades
#scrape_artist_decades <- function(driver, artist_name) {
#  # Find the search input field by its CSS selector and enter the artist name
#  search_input <- driver$findElement(using = "css selector", value = ".siteSearchInput")
#  search_input$sendKeysToElement(list(artist_name))
  
#  # Find and click the search button
# search_button <- driver$findElement(using = "css selector", value = ".siteSearchButton")
#  search_button$clickElement()
  
#  if (artist_name == "Diana Ross & The Supremes") {
#    # Find and click the specified artist filter
#   element_to_click <- driver$findElement(using = "css selector", value = ".filter > div:nth-child(2) > h3:nth-child(1) > a:nth-child(1)")
#    element_to_click$clickElement()
#  }
  
#  # Find the artist info section by its CSS selector
#  artist_info <- driver$findElement(using = "css selector", value = "div.artist:nth-child(2) > div:nth-child(1)")
  
#  # Extract the decades
#  decades <- artist_info$findElement(using = "css selector", value = "div.artist:nth-child(2) > div:nth-child(1) > div:nth-child(4)")
#  decades_text <- decades$getElementText()[[1]] %>%
#                                 str_replace("^.*\\n", "")
#  return(decades_text)
#}

# Initialize the RSelenium driver and accept cookies
#driver <- navigate_and_accept_cookies()

# List of artist names
#artist_names <- greatest_100_info$name

# Create an empty tibble to store the data
#artists_decades <- tibble(
#  name = character(0),
#  decade = character(0)
#)
#
# Loop through artist names and scrape their decades
#for (artist_name in artist_names) {
#  decades <- scrape_artist_decades(driver, artist_name)
#  artists_decades <- artists_decades %>% 
#    add_row(name = artist_name, decade = decades)
#}
# Close the driver when done
#driver$close()

#artists_decades <- artists_decades %>%
#  mutate(decade = str_extract(decade, "\\d{4}s"))

# Write artists_decades to the csv
# write.csv(artists_decades, "artist_decades.csv")
```

```{r, cache=TRUE}
# Read artists_decades
artists_decades <- read.csv("artist_decades.csv")
greatest_100_info <- greatest_100_info %>%
  left_join(select(artists_decades, name, decade), by = "name")

popularity_vs_decade <- plot_ly(data = greatest_100_info, x = ~decade, y = ~popularity) %>%
                 add_boxplot(marker = list(color = 'lightgray'), showlegend = FALSE) %>%
                 add_trace(x = ~decade, y = ~popularity, type = 'scatter', mode = 'markers',
                           marker = list(size = 10), text = ~name, hoverinfo = 'text', name = "Artists") %>%
                 layout(title = "Popularity Distribution by Decade",
                        xaxis = list(title = "Decade"),
                        yaxis = list(title = "Popularity"))
popularity_vs_decade
# Calculate mean popularity for each decade
mean_popularity_by_decade <- greatest_100_info %>%
  group_by(decade) %>%
  summarize(mean_popularity = mean(popularity, na.rm = TRUE))
```
[**Fig.2:** *The box plot shows the popularity range of artists grouped by decade.*]{style="display: block; text-align: center; font-size: small;"}

When examining the popularity of artists in 2023 based on the decade in
which they began their music careers, certain trends emerge. While the
magazine compilation includes a larger number of artists who started
their music careers in the 1960s and 1970s, it is generally observed
that artists tend to become more popular as their debut dates get closer
to the present. However, there is also an observation that rock artists
who initiated their music careers in the 1960s continue to maintain
their popularity in 2023.

```{r}
# To be commented 
# unique_common_artists <- unique_common_artists[unique_common_artists != "Neil Young"]

# Create an empty data frame to store the mean values
# mean_values_df <- data.frame()

# Loop through unique_common_artists and calculate mean values
# for (i in seq_along(unique_common_artists)) {
#   artist_id <- get_artist_id(unique_common_artists[i])
  
#   if (unique_common_artists[i] != '6v8FB84lnmJs434UJf2Mrm') {
#     artist_features <- spotifyr::get_artist_audio_features(artist_id) %>%
#       select(artist_name, danceability, energy, loudness, speechiness, acousticness, instrumentalness, tempo)
    
#     mean_values <- artist_features %>%
#       summarise(across(where(is.numeric), mean))
    
#     # Add artist_name to mean_values
#     mean_values$artist_name <- unique_common_artists[i]
    
#     # Bind the result to the mean_values_df
#     mean_values_df <- bind_rows(mean_values_df, mean_values)}
# }

#neil_tracks <- get_artist_top_tracks(get_artist_id("neil young"))
#for (id in neil_tracks$id){
#   artist_feature <- get_track_audio_features(id) %>%
#     select(danceability, energy, loudness, speechiness, acousticness, instrumentalness, tempo)
#   mean_values <- artist_feature %>%
#       summarise(across(where(is.numeric), mean))
#   mean_values$artist_name <- "Neil Young"
# }
# mean_full <- bind_rows(mean_values_df, mean_values)
# features_vs_popularity <- left_join(mean_full, select(greatest_100_info, name, popularity), by = c("artist_name" = "name"))
# Write features_vs_popularity to a CSV file
# write.csv(features_vs_popularity, "features_vs_popularity.csv", row.names = FALSE)

#not_in_billboard <- greatest_100_info$name[!(greatest_100_info$name %in% unique_common_artists)]

# Create an empty data frame to store the mean values
#mean_values_df <- data.frame()

# Loop through not_in_billboard and calculate mean values
#for (i in seq_along(not_in_billboard)) {
  #artist_id <- get_artist_id(not_in_billboard[i])
#  if (not_in_billboard[i] != '6v8FB84lnmJs434UJf2Mrm') {
#  artist_features <- spotifyr::get_artist_audio_features(artist_id) %>%
#    select(artist_name, danceability, energy, loudness, speechiness, acousticness, instrumentalness, tempo)
  
#  mean_values <- artist_features %>%
#    summarise(across(where(is.numeric), mean))
  
  # Add artist_name to mean_values
#  mean_values$artist_name <- not_in_billboard[i]
  
  # Bind the result to the mean_values_df
#  mean_values_df <- bind_rows(mean_values_df, mean_values)
#  }}
#not_in_billboard_features <- left_join(mean_values_df, select(greatest_100_info, name, popularity), by = c("artist_name" = "name"))
#not_in_billboard_features$genre <- greatest_100_info$genres[greatest_100_info$name %in% not_in_billboard_features$artist_name]
#not_in_billboard_features <- not_in_billboard_features %>%
#select("artist_name", "popularity", "genre", everything())
#features_vs_popularity$genre <- greatest_100_info$genres[greatest_100_info$name %in% features_vs_popularity$artist_name]
#features_vs_popularity <- features_vs_popularity %>%
#select("artist_name", "popularity", "genre", everything())
#write.csv(not_in_billboard_features, "not_in_billboard_features.csv", row.names = FALSE)
```

```{r}
# Read the CSV files
in_billboard_features <- read.csv("features_vs_popularity.csv")
in_billboard_features$genre <- greatest_100_info$genres[greatest_100_info$name %in% in_billboard_features$artist_name]
in_billboard_features <- in_billboard_features %>%
select("artist_name", "popularity", "genre", everything())
not_in_billboard_features <- read.csv("not_in_billboard_features.csv")

# Drop 'genre' column from both data frames
in_billboard_features <- in_billboard_features[, !(colnames(in_billboard_features) %in% c("genre", "X"))]
not_in_billboard_features <- not_in_billboard_features[, !colnames(not_in_billboard_features) %in% "genre"]

features_vs_popularity <- rbind(in_billboard_features, not_in_billboard_features)
```

Lyrically rich songs attract more listeners with a moderate correlation.
Faster tempo songs have lower popularity, with a weak correlation.
Energetic tracks with a fast, loud feel are more popular, despite a very
low correlation. Danceability doesn't show a clear correlation, with
highly danceable songs not necessarily being more popular, and less
danceable songs still achieving significant popularity. Thus, a
song's popularity is primarily influenced by its decade and genre rather
than specific Spotify metrics. 

[**Fig.3-7:** *Graphs illustrate correlations between artists'
popularity change and mean levels of speechiness, tempo, energy, and
danceability in their
songs.*]{style="display: block; text-align: center; font-size: small;"}

```{r, fig.width=6, fig.height=4, out.width='100%', fig.align='center'}
# Function to create a scatter plot with polynomial regression
create_feature_plot <- function(data, feature, title_suffix) {
  # Sort the data by the specified feature
  sorted_data <- data[order(data[[feature]]), ]
  
  # Create a scatter plot for the specified feature
  feature_plot <- plot_ly(sorted_data, 
                         x = ~get(feature), 
                         y = ~popularity, 
                         text = ~artist_name, 
                         type = "scatter", 
                         mode = "markers", 
                         marker = list(size = 10), 
                         name = "Actual",
                         showlegend = FALSE)

  # Fit a quadratic polynomial regression model for the specified feature
  poly_model_feature <- lm(popularity ~ poly(sorted_data[[feature]], 2), data = sorted_data)
  
  # Generate predicted values from the polynomial model for the specified feature
  predicted_values_feature <- predict(poly_model_feature, data.frame(energy = sorted_data[[feature]]))
  
  # Add polynomial regression line to the plot for the specified feature
  feature_plot <- feature_plot %>% 
    add_trace(x = sorted_data[[feature]], 
              y = predicted_values_feature, 
              type = "scatter", 
              mode = 'lines+markers', 
              line = list(color = "blue"), 
              name = paste("Predicted", tools::toTitleCase(feature)))

  # Customize layout for the plot
  layout <- list(xaxis = list(title = tools::toTitleCase(feature)),
                 yaxis = list(title = "Popularity"))
  
  # Apply the layout
  feature_plot <- feature_plot %>% layout(layout)
  
  return(feature_plot)
}

# Create plot the "speechiness" feature
speechiness_vs_pop <- create_feature_plot(features_vs_popularity, "speechiness")%>% layout(title = "Popularity Trends Across Song Speechiness Level" , xaxis = list(title = "Speechiness"), yaxis = list(title = "Popularity"))
```

```{r, fig.width=6, fig.height=4, out.width='100%', fig.align='center'}

# Show the plot
speechiness_vs_pop

# Create plot the "tempo" feature
tempo_vs_pop <- create_feature_plot(features_vs_popularity, "tempo")%>% layout(title = "Popularity Trends Across Song Tempo Level" , xaxis = list(title = "Tempo"), yaxis = list(title = "Popularity"))

# Show the plot
tempo_vs_pop
```

```{r, fig.width=6, fig.height=4, out.width='100%', fig.align='center'}
# Create plot the "energy" feature
energy_vs_pop <- create_feature_plot(features_vs_popularity, "energy", "Billboard") %>% layout(title = "Popularity Trends Across Song Energy Levels" , xaxis = list(title = "Energy"), yaxis = list(title = "Popularity"))

energy_vs_pop
# Create plot for the "danceability" feature
danceability_vs_pop <- create_feature_plot(features_vs_popularity, "danceability") %>% 
  layout(title = "Popularity Trends Across Song Danceability Levels", 
         xaxis = list(title = "Danceability"), 
         yaxis = list(title = "Popularity"))

danceability_vs_pop
```

```{r, cache =TRUE}
# Function to retrieve Billboard data
get_billboard_data <- function(url) {
  # Start the Selenium server
  rD <- rsDriver(browser = "firefox", verbose = FALSE, port = netstat::free_port(random = TRUE), chromever = NULL)
  driver <- rD[["client"]]
  
  # Specify the URL of the Billboard Artist 100 chart
  driver$navigate(url)
  
  # Wait for the page to load
  Sys.sleep(1)
  
  # Extract the HTML content of the entire page
  page_source <- driver$getPageSource()
  
  # Parse the HTML content with rvest
  page <- read_html(page_source[[1]])
  
  # Create a sequence from 1 to 100
  ranks <- seq(1, 100)
  
  # Extract the names
  names <- page %>%
    html_nodes("li.o-chart-results-list__item h3.c-title") %>%
    html_text() %>%
    gsub("^\\s+|\\s+$", "", .)
  
  # Create a data frame to store the data
  billboard_data <- data.frame(Rank = ranks, name = names)
  
  # Close the Selenium connection
  rD[["server"]]$stop()
  
  return(billboard_data)}

# Specify the base URL
base_url <- "https://www.billboard.com/charts/artist-100/2023-"

# Define the months
months <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")

# Initialize a list to store the data for each month
billboard_data_list <- list()

# Retrieve Billboard data for each month
for (month in months) {
  # Construct the URL for the current month
  url <- paste0(base_url, month, "-23/")
  
  # Retrieve Billboard data for the current month
  billboard_data <- get_billboard_data(url)
  
  # Store the data in the list
  billboard_data_list[[month]] <- billboard_data
}

# Function to compare common artists
compare_common_artists <- function(greatest_100, billboard_data) {
  # Find common artists
  common_artists <- greatest_100$name[greatest_100$name %in% billboard_data$name]
  return(common_artists)
}

# Initialize an empty list to store common artists for each month
common_artists_list <- list()

# Compare common artists for each month
for (i in seq_along(billboard_data_list)) {
  common_artists <- compare_common_artists(greatest_100, billboard_data_list[[i]])
  common_artists_list[[i]] <- common_artists
}

# Count the number of common artists for each month
common_counts <- sapply(common_artists_list, length)

# Create a data frame for plotting
billboard_artist_counts <- data.frame(Month = month.name, Count = common_counts)

# Create an empty list to store hover text
hover_text <- list()

# Loop through each month and update the hover text
for (i in seq_along(common_artists_list)) {
  hover_text[[i]] <- paste("Common Artists:\n", paste(common_artists_list[[i]], collapse = "\n"))
}

# Create an interactive line graph
greatest_vs_billboard <- plot_ly(billboard_artist_counts , x = ~Month, y = ~Count, type = 'scatter', mode = 'lines+markers',
                marker = list(size = 10, color = 'rgba(219, 38, 38, 0.7)'),
                text = hover_text,
                hoverinfo = 'text') %>% layout(
  hovermode = 'closest',
  showlegend = FALSE,
  hoverlabel = list(bgcolor = 'white'),
  xaxis = list(categoryorder = "array", categoryarray = month.name),
  yaxis = list(range = c(0, max(common_counts) + 1)),
  title = list(text = "The Artists who entered the Billboard Chart in 2023", font = list(size = 16), yanchor = "top", y = 0.95)
)
greatest_vs_billboard
```
```{r}
# Initialize an empty vector to store unique common artists
 unique_common_artists <- character(0)

 #Loop through each month and update the vector
 for (i in seq_along(billboard_data_list)) {
  common_artists_month <- compare_common_artists(greatest_100, billboard_data_list[[i]])
   unique_common_artists <- union(unique_common_artists, common_artists_month)
}

# Convert to a data frame
billboard_artists <- data.frame(artist = unique_common_artists, stringsAsFactors = FALSE) %>%
                    left_join(greatest_100_info, by = c("artist" = "name"))

decade_counts <- billboard_artists %>%
  group_by(decade) %>%
  summarize(count = n())

genre_counts_billboard <- billboard_artists %>%
  group_by(genres) %>%
  summarise(count = n())
```

[**Fig.8:** *The line graph illustrates the number of artists featured
in the Billboard Artist 100 Chart. (Data is extracted from the third
week of each
month.)*]{style="display: block; text-align: center; font-size: small;"}

<br>

Billboard Artist 100 charts reveal insights into artists' endurance.
Despite monthly fluctuations, only 24 artists consistently appeared
throughout 2023. Reviewing artists on the Billboard list, mostly artists from more latter decades and rock artists
debuted in 60s are present in the list in line with the analysis. However, country and blues
artists struggle to gain entry.  

In conclusion, laterly debuted and artists in contemporary genres such as rock and rap maintain higher popularity levels. Additionally, songs with more lyrics contribute to increased popularity in 2023. Richly lyrical songs also contribute to increased popularity in 2023. 


<center>[**BIBLIOGRAPHY**]{style="color:black"}</center>

<br>

Spotify. (n.d.). Spotify Web API. Retrieved December 27, 2023, from
<https://developer.spotify.com/documentation/web-api/>

Rolling Stone. (2010, December 3). 100 Greatest Artists: The Beatles,
Eminem and more of the best of the best. Retrieved December 27, 2023,
from
<https://www.rollingstone.com/music/music-lists/100-greatest-artists-147446/jimi-hendrix-5-30413/>

Billboard. (n.d.). Billboard Artist 100. Retrieved December 29, 2023,
from <https://www.billboard.com/charts/artist-100/>

All Music (n.d.) All Music etrieved December 31, 2023, from
www.allmusic.com \## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
