---
title: "Final Assignment"
author: "Dr Thomas Robinson and Dr Dan de Kadt"
date: "AT 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # actually set the global chunk options.
```

```{r, include=FALSE}
library(spotifyr)
library(dplyr)
library(httr)
library(jsonlite)
library(plotly)
library(RSelenium)
library(rvest)
library(ggplot2)
```

**INTRODUCTION:**

This report explores the current state of music of artists listed by Rolling Stone Magazine in 2010 and aims to uncover characteristics illuminating their enduring engagements. The study employs Spotify followers and popularity scores to quantify listener engagement. Additionally, it examines how many artists entered the Billboard Artist 100 Charts throughout the year and their genre distributions. The hypothesis suggests that genre influences popularity, proposing that artists in contemporary genres like rap and rock maintain high engagement, whereas genres like blues and soul, with a limited audience today, are less popular. The study also explores song features of artists, seeking correlations with ongoing popularity despite the 13-year span.

**DATA:**

Three primary sources were used for analysis: Rolling Stone's list, Billboard Charts, and the Spotify Web API.

Rolling Stone's compilation, forming the basis of the study, was collected in segments due to the dynamic loading of the website. After the top 50 were loaded, the top 50 were scraped by simulating clicks on the 50-41 ranking range in RSelenium, and then these datasets were combined in 'greatest_100' .

Billboard ranks artists based on popularity metrics like sales, streaming, and media presence. To assess the current popularity of artists on Rolling Stone magazine, I found it useful to examine how many artists have made these lists through 2023 and designed 'get_billboard_data' to extract chart data. Notably, Billboard publishes charts weekly rather than monthly, leading me to specifically extract data from the 3rd week of each month as representative. Utilizing another helper function and a for loop, common artists with the Rolling Stone ranking are gathered.

The Spotifyr package's detailed functions prompted defining new refined functions for Spotify API access. The 'get_artist_info' retrieves genres, popularity, and total followers. Applied to 'greatest_100' with a for loop and an if statement for naming inconsistencies, sub-genres are grouped for clarity. The 'get_artist_id' helper function used with 'get_artist_audio_features', calculating track feature averages. A bug arose for Neil Young, lacking Spotify albums, addressed by averaging features of singles.

After data processing, four primary analysis datasets were generated:

- 'greatest_100_info': Contains artists' names, genres, popularity scores, followers, and Rolling Stone rankings.
- 'features_vs_popularity' or 'not_in_billboard_features': Includes average values of artists' music features, categorized based on Billboard inclusion.
- 'billboard_artists': Names and genres of artists appearing in both Billboard Charts and Rolling Stone rankings.

```{r, include=FALSE, cache = TRUE}
# Start the Selenium server
#rD <- rsDriver(browser = "firefox", verbose = FALSE, port = netstat::free_port(random = TRUE), chromever = NULL)
#driver <- rD[["client"]]

# Specify the URL of the Rolling Stone page
#rank_url <- "https://www.rollingstone.com/music/music-lists/100-greatest-artists-147446/"
#driver$navigate(rank_url)

# Find the "Reject All" button and click it
#reject_button <- driver$findElement(using = "css", value = "#onetrust-reject-all-handler")
#reject_button$clickElement()

# Extract the HTML content of the entire page
#page_source <- driver$getPageSource()

# Parse the HTML content with rvest
#page <- read_html(page_source[[1]])

# Extract rank and name information
#rank_elements <- page %>% html_nodes("span.c-gallery-vertical-album__number")
#name_elements <- page %>% html_nodes("h2.c-gallery-vertical-album__title")

# Extract text from HTML nodes
#ranks <- html_text(rank_elements)
#names <- html_text(name_elements)

# Create a data frame with rank and name
#artists_data <- data.frame(
#  rank = as.integer(ranks),
#  name = names,
#  stringsAsFactors = FALSE
#)

#webElem <- driver$findElement("css", "body")
#webElem$sendKeysToElement(list(key = "end"))

# Wait for some time to let the page load
#Sys.sleep(5)

# Click on the "50 - 41" link to load the next set of artists
#driver$findElement(using = "link text", value = "50 - 41")$clickElement()

# Wait for some time after clicking to allow content to load
#Sys.sleep(5)

# Extract the HTML content of the page after clicking
#page_source_next <- driver$getPageSource()

# Parse the HTML content with rvest for the next set of artists
#page_next <- read_html(page_source_next[[1]])

# Extract rank and name information for the next set of artists
#rank_elements_next <- page_next %>% html_nodes("span.c-gallery-vertical-album__number")
#name_elements_next <- page_next %>% html_nodes("h2.c-gallery-vertical-album__title")

# Extract text from HTML nodes for the next set of artists
#ranks_next <- html_text(rank_elements_next)
#names_next <- html_text(name_elements_next)

# Create a data frame for the next set of artists
#artists_data_next <- data.frame(
#  rank = as.integer(ranks_next),
#  name = names_next,
#  stringsAsFactors = FALSE
#)
# Close the RSelenium server
#rD[["server"]]$stop()

# Merge the data frames using rbind
#greatest_100 <- rbind(artists_data, artists_data_next)
#write.csv(greatest_100, file = "greatest_100.csv", row.names = FALSE)
greatest_100 <- read.csv("greatest_100.csv")
```

```{r,, include=FALSE, cache = TRUE}
readRenviron("~/Desktop/myenvs/spotify.env")

apikey <- Sys.getenv("SPOTIFY_CLIENT_SECRET")
access_token <- get_spotify_access_token()

# Function to get artist information by name
get_artist_info <- function(artist_name) {
  access_token <- get_spotify_access_token()
  
  # Spotify API endpoint for artists
  artist_endpoint <- paste0("https://api.spotify.com/v1/search?q=",
                            URLencode(artist_name), "&type=artist&limit=1")
  
  # Make GET request to the Spotify API
  response <- GET(
    url = artist_endpoint,
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  stop_for_status(response)
  
  # Parse JSON response
  artist_info <- content(response, "parsed")
  
  # Extract relevant information
  artist_data <- data.frame(
    name = artist_info$artists$items[[1]]$name,
    genres = toString(artist_info$artists$items[[1]]$genres),
    popularity = toString(artist_info$artists$items[[1]]$popularity),
    followers_total = artist_info$artists$items[[1]]$followers$total,
    stringsAsFactors = FALSE
  )
  
  return(artist_data)
}

# Function to get artist ID by name
get_artist_id <- function(artist_name) {
  access_token <- get_spotify_access_token()
  
  # Spotify API endpoint for artists
  artist_endpoint <- paste0("https://api.spotify.com/v1/search?q=",
                            URLencode(artist_name), "&type=artist&limit=1")
  
  # Make GET request to the Spotify API
  response <- GET(
    url = artist_endpoint,
    add_headers(Authorization = paste("Bearer", access_token))
  )
  stop_for_status(response)
  
  # Parse JSON response
  artist_info <- content(response, "parsed")
  
  # Extract relevant information
  artist_id <- artist_info$artists$items[[1]]$id
  
  return(artist_id)
}

function(artist_id, country_code = "US") {
  access_token <- get_spotify_access_token()
  endpoint <- paste0("https://api.spotify.com/v1/artists/", artist_id, "/top-tracks")
  
  response <- GET(
    endpoint,
    add_headers("Authorization" = paste("Bearer", access_token)),
    query = list(country = country_code, limit = 10),
    verbose()
  )
  
  stop_for_status(response)
  
  tracks_data <- content(response)$tracks
  
  tracks_df <- data.frame(
    name = sapply(tracks_data, function(track) track$name),
    popularity = sapply(tracks_data, function(track) track$popularity),
    id = sapply(tracks_data, function(track) track$id),

    stringsAsFactors = FALSE
  )
  
  return(tracks_df)
}
```
**ANALYSIS:**

```{r, cache = TRUE}
# Create an empty list to store the results
artist_info_list <- list()

# Iterate over each row in greatest_100
for (i in 1:nrow(greatest_100)) {
  # Get the artist name and rank from the current row
  artist_name <- greatest_100$name[i]
  artist_rank <- greatest_100$rank[i]
  
  # Handle the special case for "Parliament and Funkadelic"
  if (artist_name == "Parliament and Funkadelic") {
    # Call get_artist_info("Parliament") and store the result
    artist_info <- get_artist_info("Parliament")
  } else {
    # Call get_artist_info() with the current artist name and store the result
    artist_info <- get_artist_info(artist_name)
  }
  
  # Add the rank to the artist_info data frame
  artist_info$rank <- artist_rank
  
  # Add the result to the list
  artist_info_list[[i]] <- artist_info
}

# Convert the list of data frames to a single data frame
greatest_100_info <- do.call(rbind, artist_info_list)



greatest_100_info <- greatest_100_info %>%
  mutate(genres = case_when(
    grepl("reggae", tolower(genres)) ~ "reggae",
    grepl("hip-hop", tolower(genres)) | grepl("hip hop", tolower(genres)) | grepl("rap", tolower(genres)) ~ "rap",
    grepl("rock", tolower(genres)) | grepl("punk", tolower(genres)) ~ "rock",
    grepl("blues", tolower(genres)) ~ "blues",
    grepl("soul", tolower(genres)) | grepl("motown", tolower(genres)) ~ "soul",
    grepl("pop", tolower(genres)) ~ "pop",
    TRUE ~ genres
  )) %>%  
mutate(genres = ifelse(name == "Muddy Waters", "blues", genres),
         genres = ifelse(name == "The Drifters", "blues", genres),
         genres = ifelse(name == "The Shirelles", "soul", genres),
         genres = ifelse(name == "Jackie Wilson", "soul", genres),
         genres = ifelse(name == "Michael Jackson", "pop", genres))


greatest_100_info$popularity <- as.numeric(greatest_100_info$popularity)

# Create the bubble chart
popularity_vs_genre <- plot_ly(
  data = greatest_100_info,
  x = ~rank,
  y = ~popularity,
  type = "scatter",
  text = ~name,
  color = ~genres,
  mode = "markers",
  size = ~followers_total,
  fill = ~'',
  marker = list(sizemode = "diameter", opacity = 0.7),
  colors = viridis::viridis(20)
) %>%
  layout(
    title = "Artist Popularity and Follower Counts",
    xaxis = list(
      title = "Rolling Stone Ranking",
      range = c(-5, max(greatest_100_info$rank) + 5),
      zeroline = FALSE
    ),
    yaxis = list(
      title = "Popularity Score",
      range = c(0, max(greatest_100_info$popularity) + 15),tickmode = "linear", 
      dtick = 10 
    ),
    showlegend = TRUE
  )

# Show the chart
popularity_vs_genre
```


```{r, cache =TRUE}
# Function to retrieve Billboard data
get_billboard_data <- function(url) {
  # Start the Selenium server
  rD <- rsDriver(browser = "firefox", verbose = FALSE, port = netstat::free_port(random = TRUE), chromever = NULL)
  driver <- rD[["client"]]
  
  # Specify the URL of the Billboard Artist 100 chart
  driver$navigate(url)
  
  # Wait for the page to load
  Sys.sleep(1)
  
  # Extract the HTML content of the entire page
  page_source <- driver$getPageSource()
  
  # Parse the HTML content with rvest
  page <- read_html(page_source[[1]])
  
  # Create a sequence from 1 to 100
  ranks <- seq(1, 100)
  
  # Extract the names
  names <- page %>%
    html_nodes("li.o-chart-results-list__item h3.c-title") %>%
    html_text() %>%
    gsub("^\\s+|\\s+$", "", .)
  
  # Create a data frame to store the data
  billboard_data <- data.frame(Rank = ranks, name = names)
  
  # Close the Selenium connection
  rD[["server"]]$stop()
  
  return(billboard_data)}

# Specify the base URL
base_url <- "https://www.billboard.com/charts/artist-100/2023-"

# Define the months
months <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")

# Initialize a list to store the data for each month
billboard_data_list <- list()

# Retrieve Billboard data for each month
for (month in months) {
  # Construct the URL for the current month
  url <- paste0(base_url, month, "-23/")
  
  # Retrieve Billboard data for the current month
  billboard_data <- get_billboard_data(url)
  
  # Store the data in the list
  billboard_data_list[[month]] <- billboard_data
}

# Function to compare common artists
compare_common_artists <- function(greatest_100, billboard_data) {
  # Find common artists
  common_artists <- greatest_100$name[greatest_100$name %in% billboard_data$name]
  return(common_artists)
}

# Initialize an empty list to store common artists for each month
common_artists_list <- list()

# Compare common artists for each month
for (i in seq_along(billboard_data_list)) {
  common_artists <- compare_common_artists(greatest_100, billboard_data_list[[i]])
  common_artists_list[[i]] <- common_artists
}

# Count the number of common artists for each month
common_counts <- sapply(common_artists_list, length)

# Create a data frame for plotting
billboard_artist_counts <- data.frame(Month = month.name, Count = common_counts)

# Create an empty list to store hover text
hover_text <- list()

# Loop through each month and update the hover text
for (i in seq_along(common_artists_list)) {
  hover_text[[i]] <- paste("Common Artists:\n", paste(common_artists_list[[i]], collapse = "\n"))
}

# Create an interactive line graph
greatest_vs_billboard <- plot_ly(billboard_artist_counts , x = ~Month, y = ~Count, type = 'scatter', mode = 'lines+markers',
                marker = list(size = 10, color = 'rgba(219, 38, 38, 0.7)'),
                text = hover_text,
                hoverinfo = 'text') %>% layout(
  hovermode = 'closest',
  showlegend = FALSE,
  hoverlabel = list(bgcolor = 'white'),
  xaxis = list(categoryorder = "array", categoryarray = month.name),
  yaxis = list(range = c(0, max(common_counts) + 1)),
  title = list(text = "The Artists who entered the Billboard Chart in 2023", font = list(size = 16), yanchor = "top", y = 0.95)
)

greatest_vs_billboard
```

<center><span style="color:black">The graph illustrates the number of artists featured in the Billboard Artist 100 Chart.

(Data is extracted from the chart of the third week of each month.).</span></center>



```{r}
# Initialize an empty vector to store unique common artists
 unique_common_artists <- character(0)

 #Loop through each month and update the vector
 for (i in seq_along(billboard_data_list)) {
  common_artists_month <- compare_common_artists(greatest_100, billboard_data_list[[i]])
   unique_common_artists <- union(unique_common_artists, common_artists_month)
}

# Convert to a data frame
billboard_artists <- data.frame(artist = unique_common_artists, stringsAsFactors = FALSE)
billboard_artists$genre <- greatest_100_info$genres[match(billboard_artists$artist, greatest_100_info$name)]


# Calculate genre counts for greatest_100_info
genre_counts_greatest <- greatest_100_info %>%
  group_by(genres) %>%
  summarise(count = n()) %>%
  rename(genre = genres)
genre_counts_billboard <- billboard_artists %>%
  group_by(genre) %>%
  summarise(count = n(), artists = paste(artist, collapse = "<br>"))

# Combine genre_counts_billboard and genre_counts_greatest
combined_genre_count <- merge(genre_counts_billboard, genre_counts_greatest, by = "genre", all.x = TRUE)

# Calculate proportion
combined_genre_count$proportion <- combined_genre_count$count.x / combined_genre_count$count.y * 100

# Create a ggplot bar plot
gg_bar <- ggplot(combined_genre_count, aes(x = genre, y = proportion, fill = genre, text = paste("Proportion: ", scales::percent(proportion / 100),
                                                                                                  "<br>Count: ", count.x,
                                                                                                  "<br>Artists: ", artists))) +
  geom_bar(stat = "identity") +
  labs(title = "Genre Distribution for Billboard Artists",
       x = "Genre",
       y = "Proportion") +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) 

# Convert ggplot to Plotly
combined_genre_dist <- ggplotly(gg_bar, tooltip = "text")

# Display the plot
combined_genre_dist
```

```{r}
# To be commented 
# unique_common_artists <- unique_common_artists[unique_common_artists != "Neil Young"]

# Create an empty data frame to store the mean values
# mean_values_df <- data.frame()

# Loop through unique_common_artists and calculate mean values
# for (i in seq_along(unique_common_artists)) {
#   artist_id <- get_artist_id(unique_common_artists[i])
  
#   if (unique_common_artists[i] != '6v8FB84lnmJs434UJf2Mrm') {
#     artist_features <- spotifyr::get_artist_audio_features(artist_id) %>%
#       select(artist_name, danceability, energy, loudness, speechiness, acousticness, instrumentalness, tempo)
    
#     mean_values <- artist_features %>%
#       summarise(across(where(is.numeric), mean))
    
#     # Add artist_name to mean_values
#     mean_values$artist_name <- unique_common_artists[i]
    
#     # Bind the result to the mean_values_df
#     mean_values_df <- bind_rows(mean_values_df, mean_values)}
# }

# neil_tracks <- get_artist_top_tracks(get_artist_id("neil young"))
# for (id in neil_tracks$id){
#   artist_feature <- get_track_audio_features(id) %>%
#     select(danceability, energy, loudness, speechiness, acousticness, instrumentalness, tempo)
#   mean_values <- artist_feature %>%
#       summarise(across(where(is.numeric), mean))
#   mean_values$artist_name <- "Neil Young"
# }

# mean_full <- bind_rows(mean_values_df, mean_values)
# features_vs_popularity <- left_join(mean_full, select(greatest_100_info, name, popularity), by = c("artist_name" = "name"))
# Write features_vs_popularity to a CSV file
# write.csv(features_vs_popularity, "features_vs_popularity.csv", row.names = FALSE)

#not_in_billboard <- greatest_100_info$name[!(greatest_100_info$name %in% unique_common_artists)]

# Create an empty data frame to store the mean values
#mean_values_df <- data.frame()

# Loop through not_in_billboard and calculate mean values
#for (i in seq_along(not_in_billboard)) {
  #artist_id <- get_artist_id(not_in_billboard[i])
#  if (not_in_billboard[i] != '6v8FB84lnmJs434UJf2Mrm') {
#  artist_features <- spotifyr::get_artist_audio_features(artist_id) %>%
#    select(artist_name, danceability, energy, loudness, speechiness, acousticness, instrumentalness, tempo)
  
#  mean_values <- artist_features %>%
#    summarise(across(where(is.numeric), mean))
  
  # Add artist_name to mean_values
#  mean_values$artist_name <- not_in_billboard[i]
  
  # Bind the result to the mean_values_df
#  mean_values_df <- bind_rows(mean_values_df, mean_values)
#  }}
#not_in_billboard_features <- left_join(mean_values_df, select(greatest_100_info, name, popularity), by = c("artist_name" = "name"))
#not_in_billboard_features$genre <- greatest_100_info$genres[greatest_100_info$name %in% not_in_billboard_features$artist_name]
#not_in_billboard_features <- not_in_billboard_features %>%
#select("artist_name", "popularity", "genre", everything())
#features_vs_popularity$genre <- greatest_100_info$genres[greatest_100_info$name %in% features_vs_popularity$artist_name]
#features_vs_popularity <- features_vs_popularity %>%
#select("artist_name", "popularity", "genre", everything())
#write.csv(not_in_billboard_features, "not_in_billboard_features.csv", row.names = FALSE)
```

```{r}
features_vs_popularity <- read.csv("features_vs_popularity.csv")
not_in_billboard_features<- read.csv("not_in_billboard_features.csv")
```

```{r}
# Function to create a scatter plot with polynomial regression
create_feature_plot <- function(data, feature, title_suffix) {
  # Sort the data by the specified feature
  sorted_data <- data[order(data[[feature]]), ]
  
  # Create a scatter plot for the specified feature
  feature_plot <- plot_ly(sorted_data, 
                         x = ~get(feature), 
                         y = ~popularity, 
                         text = ~artist_name, 
                         type = "scatter", 
                         mode = "markers", 
                         marker = list(size = 10), 
                         name = "Actual",
                         showlegend = FALSE)

  # Fit a quadratic polynomial regression model for the specified feature
  poly_model_feature <- lm(popularity ~ poly(sorted_data[[feature]], 2), data = sorted_data)
  
  # Generate predicted values from the polynomial model for the specified feature
  predicted_values_feature <- predict(poly_model_feature, data.frame(energy = sorted_data[[feature]]))
  
  # Add polynomial regression line to the plot for the specified feature
  feature_plot <- feature_plot %>% 
    add_trace(x = sorted_data[[feature]], 
              y = predicted_values_feature, 
              type = "scatter", 
              mode = 'lines+markers', 
              line = list(color = "blue"), 
              name = paste("Predicted", tools::toTitleCase(feature)))

  # Customize layout for the plot
  layout <- list(xaxis = list(title = tools::toTitleCase(feature)),
                 yaxis = list(title = "Popularity"))
  
  # Apply the layout
  feature_plot <- feature_plot %>% layout(layout)
  
  return(feature_plot)
}

# Create plots for both billboard and non-billboard data with the "energy" feature
energy_vs_pop_billboard <- create_feature_plot(features_vs_popularity, "energy", "Billboard")
energy_vs_pop_notbillboard <- create_feature_plot(not_in_billboard_features, "energy", "Non-Billboard")

# Combine both plots
energy_vs_pop_combined <- subplot(energy_vs_pop_billboard, energy_vs_pop_notbillboard, nrows = 2, shareX = TRUE, titleX = FALSE, titleY = FALSE, margin = 0.05) %>% layout(title = "Popularity Trends Across Song Energy Levels" , xaxis = list(title = "Energy"), yaxis = list(title = "Popularity"))
# Show the combined plot
energy_vs_pop_combined

```

```{r, fig.align="center"}
# Create plots for both billboard and non-billboard data with the "danceability" feature
danceability_vs_pop_billboard <- create_feature_plot(features_vs_popularity, "danceability", "Billboard")
danceability_vs_pop_notbillboard <- create_feature_plot(not_in_billboard_features, "danceability", "Non-Billboard")

# Combine both plots
danceability_vs_pop_combined <- subplot(danceability_vs_pop_billboard, danceability_vs_pop_notbillboard, nrows = 2, shareX = TRUE, titleX = FALSE, titleY = FALSE, margin = 0.05) %>% layout(title = "Popularity Trends Across Song Danceability Levels" , xaxis = list(title = "Danceability"), yaxis = list(title = "Popularity"))
# Show the combined plot
danceability_vs_pop_combined
```

```{r}
# Create plots for both billboard and non-billboard data with the "instrumentalness" feature
instrumentalness_vs_pop_billboard <- create_feature_plot(features_vs_popularity, "instrumentalness", "Billboard")
instrumentalness_vs_pop_notbillboard <- create_feature_plot(not_in_billboard_features, "instrumentalness", "Non-Billboard")

# Combine both plots
instrumentalness_vs_pop_combined <- subplot(instrumentalness_vs_pop_billboard, instrumentalness_vs_pop_notbillboard, nrows = 2, shareX = TRUE, titleX = FALSE, titleY = FALSE, margin = 0.05) %>% layout(title = "Popularity Trends Across Song Instrumentalness Level" , xaxis = list(title = "Instrumentalness"), yaxis = list(title = "Popularity"))

# Show the combined plot
instrumentalness_vs_pop_combined
```

```{r}
# Create plots for both billboard and non-billboard data with the "tempo" feature
tempo_vs_pop_billboard <- create_feature_plot(features_vs_popularity, "tempo", "Billboard")
tempo_vs_pop_notbillboard <- create_feature_plot(not_in_billboard_features, "tempo", "Non-Billboard")

# Combine both plots
tempo_vs_pop_combined <- subplot(tempo_vs_pop_billboard, tempo_vs_pop_notbillboard, nrows = 2, shareX = TRUE, titleX = FALSE, titleY = FALSE, margin = 0.05) %>% layout(title = "Popularity Trends Across Song Tempo Level" , xaxis = list(title = "Tempo"), yaxis = list(title = "Popularity"))

# Show the combined plot
tempo_vs_pop_combined
```

```{r}
# Create plots for both billboard and non-billboard data with the "speechiness" feature
speechiness_vs_pop_billboard <- create_feature_plot(features_vs_popularity, "speechiness", "Billboard")
speechiness_vs_pop_notbillboard <- create_feature_plot(not_in_billboard_features, "speechiness", "Non-Billboard")

# Combine both plots
speechiness_vs_pop_combined <- subplot(speechiness_vs_pop_billboard, speechiness_vs_pop_notbillboard, nrows = 2, shareX = TRUE, titleX = FALSE, titleY = FALSE, margin = 0.05) %>% layout(title = "Popularity Trends Across Song Speechiness Level" , xaxis = list(title = "Speechiness"), yaxis = list(title = "Popularity"))

# Show the combined plot
speechiness_vs_pop_combined
```

```{r}
# Create plots for both billboard and non-billboard data with the "acousticness" feature
acousticness_vs_pop_billboard <- create_feature_plot(features_vs_popularity, "acousticness", "Billboard")
acousticness_vs_pop_notbillboard <- create_feature_plot(not_in_billboard_features, "acousticness", "Non-Billboard")

# Combine both plots
acousticness_vs_pop_combined <- subplot(acousticness_vs_pop_billboard, acousticness_vs_pop_notbillboard, nrows = 2, shareX = TRUE, titleX = FALSE, titleY = FALSE, margin = 0.05)%>% layout(title = "Popularity Trends Across Song Acousticness Level" , xaxis = list(title = "Acousticness"), yaxis = list(title = "Popularity"))

# Show the combined plot
acousticness_vs_pop_combined
```
## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```